---
title: "Faith in institutions over time"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
require(haven)
require(stringr)
```

# Code

See the code along with brief explanations in [the other markdown doc](LINK).

```{r code=xfun::read_utf8('../tools/mapping-variable-names-to-labels/create-mapping.R'), include=FALSE}
```

```{r code=xfun::read_utf8('../tools/creating-datasets/get-specific-data-by-years.R'), include=FALSE}
```

```{r code=xfun::read_utf8('../tools/visualization/plot-prevalence-over-time.R'), include=FALSE}
```

# Trends over time: faith in institutions

Set up the code by creating a smaller database that includes only the "faith in institutions" questions and demographic markers that I might later sort by.

```{r}
demographics = c("R'S ID-SERIAL #",
                 "SAMPLING WEIGHT",
                 "R'S SEX",
                 "R'S POLTL PRFNC",
                 "R'S RACE",
                 "R'S RACE B/W/H"
                 )

institutions = c("GD JB PRES&ADMIN",
                 "GD JB CONGRESS",
                 "GD JB SUPRM CRT",
                 "GD JB JUSTC SYST",
                 "GD JB POLICE",
                 "GD JB MILITARY",
                 "GD JB PBLC SCHOL",
                 "GD JB COLLG&UNIV",
                 "GD JB CHURCHES",
                 "GD JB NEWS MEDIA",
                 "GD JB LARG CORPS",
                 "GD JB LBR UNIONS")

institution_labels = c("The President and his administration",
                       "Congress",
                       "The U.S. Supreme Court",
                       "All the courts and the justice system in general",
                       "The police and other law enforcement agencies",
                       "The U.S. military",
                       "The nation's public schools",
                       "The nation's colleges and universities",
                       "Churches and religious organizations",
                       "The national news media",
                       "Large corporations",
                       "Major labor unions")

```

``` {r}
grade12_file4_mapping = tibble()

for (year in 1990:2018) {
  grade12_file4_mapping = rbind(grade12_file4_mapping,
                                create_mapping(path = "~/Documents/Code/MTF/MTFData/12th_grade/",
                                               year = year,
                                               file_number = 4
                                )
  )
}
```

```{r}
smallDB = get_specific_data_by_years(path = "~/Documents/Code/MTF/MTFData/12th_grade/",
                                     file_number = 4,
                                     years = 1990:2018,
                                     mapping = grade12_file4_mapping,
                                     variables_to_include = c(demographics, institutions)
                                     )
```

# How good or bad a job is being done for the country as a whole by . . .

(Graphs are of the percentage of respondents who said "fair", "good", or "very good" out of everyone who responded. The other answer choices were "poor" and "very poor".)
``` {r}
require(gridExtra)

plots = c()
for (i in 1:3) { #length(institutions)) {
  plots = c(plots, plot_prevalence_over_time(dataset = smallDB,
                            variable = institutions[i],
                            yes_codes = c("3", "4", "5"),
                            no_codes = c("1", "2"),
                            title = institution_labels[i]
                            )
  )
}

plots

grid.arrange(plots[1], plots[2], nrow=1)
```

Next steps:

* Graph by demographic or other factors
* Output multiple plots
* Tile the plots
* Adjust axes
* Dichotomize differently?

